Considering scale in multilayer animal social networks

### 2020-06-28 paper/manuscript.Rmd
fix missing 30 m from count

Increasing land cover resolution resulted in decreased availability of foraging
habitat and corresponding low connectivity of individuals at higher land cover
resolutions. Edge overlap decreased sharply between 30 m and 600 m in foraging
layers, afterwards remaining stable to 1000 m (Figure \@ref(fig:lcres) D). In
contrast, edge overlap was relatively consistent across land cover resolutions
in forest and open layers (Figure \@ref(fig:lcres) D).  Graph strength was more
variable within foraging habitat layers across land cover resolutions than open
and forest habitat layers (Figure \@ref(fig:lcres) E). The proportion of
relocations in forest (42.1% at 30 m - 48.2% at 1000 m) and open (43.3% at 30 m
- 50.3% at 1000 m) habitats increased with increasing spatial resolution, while
decreasing in foraging habitat (14.5% at 30 m - <2% at 1000 m).  <!-- TODO: 
break up -->Overall, these
results indicate the importance of matching land cover resolution to scale of
habitat selection as well as ensuring the land cover product used has a resolution fine
enough to detect landscape features and habitats relevant to study species, such
as important patchy and rare habitats.

@@

<!-- spatial -->
Habitat selection, the use of available resources or landscape features by
animals [@Manly_1993; @Boyce_1999], is a scale-dependent process [@Mayor_2009].
Social structure and habitat selection are intimately related and individuals
must share space to interact [@Webber_2018]. We found edge overlap was stable in
open and forest layers but decreasing in foraging layers with increasing spatial
scale (Figure \@ref(fig:lcres) D). Graph strength had greater individual
variation in open and foraging layers than in forest layers (Figure
\@ref(fig:lcres) E). We observed a decrease in the proportion of relocations in
foraging habitat with increasing spatial resolution (14.5% at 30 m - <2% at 1000
m). As the foraging layer had similar edge overlap and graph strength as the
open layer at 30 m spatial resolution despite having lower abundance on the
landscape (foraging: 12.8%, open: 36.9%), this result highlights the importance
of considering spatial scale when including habitat in multilayer networks.
Johnson [-@Johson_1980] identified four orders of habitat selection: (1) the
geographical range of a species, (2) the home range of an individual, the (3)
habitat patches within the home range and (4) specific resources within a
habitat patch. Kie et al. [-@Kie_2002] found that, independently, third order of
selection was insufficient for capturing landscape attributes selected for by
mule deer (*Odocoileus hemionus*), at a scale larger than their home range size.
Scales of habitat selection could be relevant for multilayer networks and our
integration of habitat within a multilayer context could be an important first
step (see Figure \@ref(fig:lcres)). Specifically, if individuals select habitats
at the home range scale, it may be relevant to assess social structure using
home range overlap. By contrast, in cases where individuals select habitats at
the patch-scale, fine-scale measures of sociality may be more relevant. Moving
past this hierarchical perspective, Mayor et al. [-@Mayor_2007] emphasized the
importance of considering a broad continuum of scales to reveal scale-dependent
selection and avoid the bias of predefined scales assumed to be associated with
certain behaviours.
<!-- spatial -->

>>>>

Increasing land cover resolution resulted in decreased availability of foraging
habitat and corresponding low connectivity of individuals at higher land cover
resolutions. Edge overlap decreased sharply between 30 m and 600 m in foraging
layers, afterwards remaining stable to 1000 m (Figure \@ref(fig:lcres) D). In
contrast, edge overlap was relatively consistent across land cover resolutions
in forest and open layers (Figure \@ref(fig:lcres) D).  Graph strength was more
variable within foraging habitat layers across land cover resolutions than open
and forest habitat layers (Figure \@ref(fig:lcres) E). The proportion of
relocations in forest (42.1% at 30 m - 48.2% at 1000 m) and open (43.3% at 30 m
- 50.3% at 1000 m) habitats increased with increasing spatial resolution, while
decreasing in foraging habitat (23.9% at 30 m - <2% at 1000 m).  <!-- TODO: 
break up -->Overall, these
results indicate the importance of matching land cover resolution to scale of
habitat selection as well as ensuring the land cover product used has a resolution fine
enough to detect landscape features and habitats relevant to study species, such
as important patchy and rare habitats.

@@

<!-- spatial -->
Habitat selection, the use of available resources or landscape features by
animals [@Manly_1993; @Boyce_1999], is a scale-dependent process [@Mayor_2009].
Social structure and habitat selection are intimately related and individuals
must share space to interact [@Webber_2018]. We found edge overlap was stable in
open and forest layers but decreasing in foraging layers with increasing spatial
scale (Figure \@ref(fig:lcres) D). Graph strength had greater individual
variation in open and foraging layers than in forest layers (Figure
\@ref(fig:lcres) E). We observed a decrease in the proportion of relocations in
foraging habitat with increasing spatial resolution (23.9% at 30 m - <2% at 1000
m). As the foraging layer had similar edge overlap and graph strength as the
open layer at 30 m spatial resolution despite having lower abundance on the
landscape (foraging: 12.8%, open: 36.9%), this highlights the importance
of considering spatial scale when including habitat in multilayer networks.
Johnson [-@Johson_1980] identified four orders of habitat selection: (1) the
geographical range of a species, (2) the home range of an individual, the (3)
habitat patches within the home range and (4) specific resources within a
habitat patch. Kie et al. [-@Kie_2002] found that, independently, third order of
selection was insufficient for capturing landscape attributes selected for by
mule deer (*Odocoileus hemionus*), at a scale larger than their home range size.
Scales of habitat selection could be relevant for multilayer networks and our
integration of habitat within a multilayer context could be an important first
step (see Figure \@ref(fig:lcres)). Specifically, if individuals select habitats
at the home range scale, it may be relevant to assess social structure using
home range overlap. By contrast, in cases where individuals select habitats at
the patch-scale, fine-scale measures of sociality may be more relevant. Moving
past this hierarchical perspective, Mayor et al. [-@Mayor_2007] emphasized the
importance of considering a broad continuum of scales to reveal scale-dependent
selection and avoid the bias of predefined scales assumed to be associated with
certain behaviours.
<!-- spatial -->
